On the presentation of orthogonal groups over polynomial rings

### 2019-01-29 dl-paper.tex
Writing down Proposition 1

Let $G \colon \catname{CRings} \to \catname{Groups}$ be a functor and $P$ its subfunctor such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$.

@@

\begin{prop}\label{characterization}
Let $S \colon \catname{CRings} \to \catname{Groups}$ be another group functor such that
 for all $R$ the group $S(R)$ is a universal central extension of $P(R)$. Then the following holds:
\begin{proplist}
 \item There is a natural isomorphism $\K_3(G, P, R) \cong \HH_3(S(R), \ZZ)$.
 \item For a ring epimorphism $R \to R/I$ there is a natural exact sequence
 \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & \HH_3(S(R), S(R/I), \ZZ).} \]
\end{proplist}
\end{prop}
\begin{proof}
 Follows from the solution of Exercises~1.8--1.9 of \cite[Chapter~IV]{Kbook} provided one notices that all the intermediate isomorphisms are natural in $R$.

>>>>

Let $G \colon \catname{CRings} \to \catname{Groups}$ be a functor preserving binary pullbacks and 
 $P$ its subfunctor such that for all $R$ the group $P(R)$ is a perfect normal subgroup of $G(R)$.

@@

\begin{prop}\label{characterization}
Let $S \colon \catname{CRings} \to \catname{Groups}$ be another group functor equipped with a natural transformation
 $\varphi \colon S \to P$ such that for all $R$ the group $S(R)$ is a universal central extension of $P(R)$. Then the following holds:
\begin{proplist}
 \item There is a natural isomorphism $\K_3(G, P, R) \cong \HH_3(S(R), \ZZ)$.
 \item There is an exact sequence natural in $(R, I)$:
 \[ \xymatrix{\K_3(G, P, R) \ar[r] & \K_3(G, P, R/I) \ar@{->>}[r] & \HH_3(S(R), S(R/I), \ZZ).} \]
\end{proplist}
\end{prop}
\begin{proof}
 The first claim follows from the solution of Exercises~1.8--1.9 of \cite[Chapter~IV]{Kbook}. %provided one verifies that all the intermediate isomorphisms are natural in $R$.

 Let us verify the second claim.
 Denote by $p_0, p_1, \Delta$ the two obvious projections and the diagonal map $\xymatrix{D_{R,I} \ar@<1pt>[r] \ar@<-2.5pt>[r] & \ar@<-4pt>[l] R}$
  and set $d_i = Sp_i$, $s = S\Delta$.
 Obviously, $d_0s = d_1 s = id_{S(R)}$. Set $G_i = \Ker(d_i)$, $S(R, I) = G_0 / [G_0, G_1]$ and denote by $\mu$ the natural map $S(R, I) \to N$ induced by $d_1$.

 Since $\varphi(G_i) \subseteq \Ker(G(p_i))$ and $G$ preserves pullbacks we conclude that $G_0 \cap G_1 \subseteq \Ker(\varphi) \colon S(D_{R, I}) \to G(D_{R, I}))$
  and hence $G_0 \cap G_1$ is a central subgroup of $S(D_{R, I})$.
 Now invoking~\cite[Proposition~6]{Lo78} we conclude that the extension $S(R, I) \to S(R)$ is a universal
  relative central extension of the coequalizer $\mathrm{coeq}(d_0, d_1)$.
